Parsing Postfix log files

### 2009-04-12 doc/logparser-glossary.tex
Dealt with some XXX items.
Ran diction and made changes based on its suggestions.

% vim: set filetype=tex :
% The contents of the glossary.
\newglossaryentry{SQLite}{name={SQLite},description={
    \textit{SQLite is a small C library that implements a self-contained,
    embeddable, zero-configuration SQL database engine.\/} SQLite is an
    \acronym{SQL} implementation focusing on correctness, simplicity, and
    speed.  Unlike other \acronym{SQL} implementations it does not require
    a separate server process, greatly simplifying deployment of an
    application utilising it.  More details can be found
    at~\urlLastChecked{http://www.sqlite.org/}{2009/02/23}.
}}

@@

\newglossaryentry{Epoch}{name={Epoch},description={
    Most operating systems store the current time and timestamps of files
    etc.\ as seconds elapsed since the epoch, the beginning of time as far
    as the operating system is concerned.  On Unix and Unix-derived systems
    the epoch is 1970/01/01 00:00:00; on other operating systems it may be
    different.
}}

@@

\newglossaryentry{hash}{name={hash},description={
    A hashing function transforms a string of characters to a number.
    There are many possible uses for the resulting number: a common usage
    is to maintain a data structure indexed by strings in an efficient
    manner.  A full description is beyond the scope of this paper, further
    information can be found at~\cite{hash-functions}.
}}

@@

\newglossaryentry{mail bomb}{name={Mail Bomb},description={
    A mail bomb occurs when an attacker sends a huge volume of mail to a
    victim.  At best a mail bomb is irritating to the victim; at worst the
    deluge of mail can be severe enough to interrupt service for the victim
    and/or other users, by causing mail to be delayed or rejected because
    the victim or the server has reached a limit, e.g.\ too many mails in
    their mailbox, or too much disk space consumed by the mail queue.
}}

\newglossaryentry{mail loop}{name={Mail Loop},description={
    Sometimes mail sent to one address must be forwarded to a different
    address instead, e.g.\ because a person has changed jobs.  A mail loop
    occurs when the chain of recipient addresses constitute a cyclic
    directed graph; the simplest example is when mail for
    \texttt{alice@example.net} is delivered to \texttt{bob@example.com},
    and mail for \texttt{bob@example.com} is delivered to
    \texttt{alice@example.net}.  Postfix adds a \texttt{Delivered-To:}
    header to all mails it delivers locally to detect mail loops, but in
    some cases this header is removed by the program that forwards the
    mail.
}}

>>>>

% vim: set filetype=tex :
% The contents of the glossary.
\newglossaryentry{SQLite}{name={SQLite},description={
    \textit{SQLite is a small C library that implements a self-contained,
    embeddable, zero-configuration SQL database engine.\/} SQLite is an
    \acronym{SQL} implementation focusing on correctness, simplicity, and
    speed.  Unlike other \acronym{SQL} implementations it does not require
    a separate server process, greatly simplifying deployment of an
    application utilising it.
}}

@@

\newglossaryentry{Epoch}{name={Epoch},description={
    Most operating systems store the current time and timestamps of files
    as seconds elapsed since the epoch, the beginning of time as far as the
    operating system is concerned.  On Unix and Unix-derived systems the
    epoch is 1970/01/01 00:00:00; on other operating systems it may be
    different.
}}

@@

\newglossaryentry{hash}{name={hash},description={
    A hashing function transforms a string of characters to a number.  A
    common usage is to maintain a data structure indexed by strings in an
    efficient manner.  A full description is beyond the scope of this
    paper, further information can be found at~\cite{hash-functions}.
}}

@@

\newglossaryentry{mail bomb}{name={Mail Bomb},description={
    A mail bomb occurs when an attacker sends a huge volume of mail to a
    victim.  At best a mail bomb is irritating to the victim; at worst the
    deluge of mail can be severe enough to interrupt service for the victim
    or other users, by causing mail to be delayed or rejected because the
    victim or the server has reached a limit, e.g.\ too many mails in their
    mailbox, or too much disk space consumed by the mail queue.
}}

\newglossaryentry{mail loop}{name={Mail Loop},description={
    Sometimes mail sent to one address must be forwarded to a different
    address instead, e.g.\ because a person has changed jobs.  A mail loop
    occurs when the chain of recipient addresses constitute a cyclic
    directed graph; e.g.\ mail for \texttt{alice@example.net} is delivered
    to \texttt{bob@example.com}, and mail for \texttt{bob@example.com} is
    delivered to \texttt{alice@example.net}.  Postfix adds a
    \texttt{Delivered-To:} header to all mails it delivers locally to
    detect mail loops, but in some cases this header is removed by the
    program that forwards the mail.
}}
